### 2012-10-24 doc/milestone_draft1.tex
Putting one sentence per line for easier version control

\begin{document}
\section{Algortihm 1: Generate Keys}

	genkey procedure generates a secret and public key.  The public key includes vectors \textbf{L} and \textbf{R} as well as $q$ and $\mathcal{U}$.

@@

\section{Algorithm 2: Initialization}
\label{initialize}

	initialize takes the secret key and the public key generated in step 1, and an empty dictionary over the universe of elements and produces

>>>>

\begin{document}
\section{Algortihm 1: Generate Keys}
genkey procedure generates a secret and public key.
The public key includes vectors \textbf{L} and \textbf{R} as well as $q$ and $\mathcal{U}$.

@@

\section{Algorithm 2: Initialization}
\label{initialize}
initialize takes the secret key and the public key generated in step 1, and an empty dictionary over the universe of elements and produces
